The Lasting Shadows of Economic Downturns

### 2024-02-14 outputs/paper/paper.qmd
update paper.qmd

---
title: "..."
author: "Heyucheng Zhang, Jiwon Choi"
thanks: "Code and data are available at: https://github.com/jwonc4602/STA302_paper2"
date: "12 February 2024"
date-format: "D MMMM YYYY"
abstract: "..."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "The Lasting Shadows of Economic Downturns"
subtitle: "Unveiling the 1980–1982 Recession's Long-Run Effects on Unemployment and Income in America"
author: "Heyucheng Zhang, Jiwon Choi"
thanks: "Code and data are available at: https://github.com/jwonc4602/Long-Run-Impacts-of-Recession"
date: "12 February 2024"
date-format: "D MMMM YYYY"
abstract: "..."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
